Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-07-09 analysis/sim/run_simpw.Rmd
pdf3

@@

>>>>

#################################

pdf("fig3_sim.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
par(mfrow=c(1,3))

@@

#################################
pdf("fig3_bars.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
barplot(prec,ylim=c(0,1.1),las=2,main="precision",ylab="")
text((1:6*1.18)-0.45,prec+0.02,labels=signif(prec,3))
barplot(rec,ylim=c(0,1.1),las=2,main="recall",ylab="")
text((1:6*1.18)-0.45,rec+0.02,labels=signif(rec,3))
barplot(f1,ylim=c(0,1.1),las=2,main="F1",ylab="")
text((1:6*1.18)-0.45,f1+0.02,labels=signif(f1,3))
dev.off()
